Estimation de la tendance-cycle avec des méthodes robustes aux points atypiques

### 2024-11-07 Article/article.qmd
xtick correction

```{r}
#| include: false
library(rjd3filters)
source("../0-functions.R", local = knitr::knit_global())
source("../0-functions-plot.R", local = knitr::knit_global())
lc_f <- lp_filter()
robust_ff <- readRDS("../data/robust_ff.rds")
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "ipi_voitures98.RDS"))
graph_est <- get_all_plots(res, y_as_plot = FALSE)
graph_est <- lapply(graph_est,function(p){
	p$CLF <- NULL
	p
})
graph_y <- plot_y(res)
graph_ci <- lapply(
	res$out, plot_confint,
	data = res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "ipi_voitures2004.RDS"))
graph_est <- get_all_plots(res, y_as_plot = FALSE)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "LS", "ipi_petrole_brut10.RDS"))
graph_est <- get_all_plots(res, y_as_plot = FALSE)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ls"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "LSLS", "retailx2008.RDS"))
graph_est <- get_all_plots(res, y_as_plot = FALSE)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["lsls"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AOLS", "immat2018.RDS"))
graph_est <- get_all_plots(res, y_as_plot = FALSE)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["aols"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "retailx2007.rds"))
graph_est <- get_all_plots(res, y_as_plot = FALSE)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "ce160v2001.rds"))
graph_est <- get_all_plots(res, y_as_plot = FALSE)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```

>>>>

```{r}
#| include: false
library(rjd3filters)
library(ggplot2)
library(patchwork)
source("../0-functions.R", local = knitr::knit_global())
source("../0-functions-plot.R", local = knitr::knit_global())
lc_f <- lp_filter()
robust_ff <- readRDS("../data/robust_ff.rds")
y_as_plot <- FALSE
add_y <- FALSE
apply_consistent_y_lims <- function(this_plot){
    num_plots <- length(this_plot$layers)
    y_lims <- lapply(1:num_plots, function(x) ggplot_build(this_plot[[x]])$layout$panel_scales_y[[1]]$range$range)
    min_y <- min(unlist(y_lims))
    max_y <- max(unlist(y_lims))
    this_plot & coord_cartesian(ylim = c(min_y, max_y))
}
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "ipi_voitures98.RDS"))
graph_est <- get_all_plots(res, y_as_plot = y_as_plot, add_y = add_y)
graph_est <- lapply(graph_est,function(p){
	p$CLF <- NULL
	p
})
graph_y <- plot_y(res)
graph_ci <- lapply(
	res$out, plot_confint,
	data = res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "ipi_voitures2004.RDS"))
graph_est <- get_all_plots(res, y_as_plot = y_as_plot, add_y = add_y)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "LS", "ipi_petrole_brut10.RDS"))
graph_est <- get_all_plots(res, y_as_plot = y_as_plot, add_y = add_y)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ls"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "LSLS", "retailx2008.RDS"))
graph_est <- get_all_plots(res, y_as_plot = y_as_plot, add_y = add_y)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["lsls"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AOLS", "immat2018.RDS"))
graph_est <- get_all_plots(res, y_as_plot = y_as_plot, add_y = add_y)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["aols"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "retailx2007.rds"))
graph_est <- get_all_plots(res, y_as_plot = y_as_plot, add_y = add_y)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```

@@

```{r}
res <- readRDS(file.path("..", "results", "AO", "ce160v2001.rds"))
graph_est <- get_all_plots(res, y_as_plot = y_as_plot, add_y = add_y)
graph_est$CLF <- NULL
graph_y <- plot_y(res)
graph_ci <- plot_confint(
	res,
	default_filter = lc_f,
	robust_f = robust_ff[["ao"]])
```
